Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-11 paper-2023-acsos-pulverization.tex
Use pdf instead svg
rename section
refine abstract

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{acronym}
\usepackage{listing-style}
\usepackage[hidelinks]{hyperref}
\usepackage{svg}

@@

\begin{abstract}
In recent years, we witnessed a radical change in the deployed form of distributed systems.
%
Modern applications are designed to be executed on very diverse devices
and to be deployed on heterogeneous infrastructures,
ranging from cloud servers to mobile and IoT devices.
%
De facto, complex distributed computation is happening across a cloud-edge continuum composed of heterogeneous devices and infrastructures.
%
The availablity of such an infrastructure opens to new possibilities in terms of better resource utilisation and performance,
but also poses new challenges to the application designer,
as the application must be conceived to be able to adapt its deployment to changing conditions.
%
In this paper we present a framework for the development of distributed systems
based on the concept of \emph{pulverisation},
which is meant to neatly separate business logic and deployment concerns,
allowing applications to be defined independent of the infrastructure they will execute upon.
%
The framework is based on a domain-specific language capturing,
in a declarative fashion,
the concepts composing a pulverised application and any potential target network,
also allowing for the specification of reconfiguration policies.
%
The framework, implemented in Kotlin multiplatform and available as open source,
is then evaluated in a small-scale real-world demo and in a city-scale simulated scenario.
\end{abstract}

@@

In this section we present a simple scenario where the pulverization framework is used to implement a crowd alert system:
we simulate a laboratory where a safety system warns people when they are too close to each other.
%
Each person is equipped with a wearable device that is able to detect the distance from other devices and send the distances data to the
alert system.
%
The people in the laboratory must observe a safety distance, and the system warns them when the distance is not respected by showing a red light
when they are too close to each other, and a green color when the distance is respected (see~\Cref{fig:crowd-alert}).
%
\begin{figure*}[ht]
    \centering
    \includesvg[width=.8\textwidth]{figures/crow-laboratory-demo.drawio.svg}
    \caption{
        Representation of the scenario described in the~\Cref{sec:small-scale-crowd-alert}
        where more the people are far from each other, more the color of the screen is green.
        More the people are close to each other, more the color of the screen is red.
        The blue dot represents the wearable device and the link between the devices represents the distance between them.
        The rectangle represents the monitor in the laboratory which shows the congestion level of the laboratory (via the color described above).
    }
    \label{fig:crowd-alert}
\end{figure*}
%
The system is composed of two kind of devices: \emph{wearable} and \emph{laboratory}.
%
The former represents the wearable devices that is worn by the people, and consists of the following pulverized components:
$\beta$, $\chi$, and $\sigma$.
%
The \emph{behaviour} ($\beta$) component is responsible for converting the raw data from the sensor into the distance
between the device and the others; the \emph{sensors} ($\sigma$) component is responsible for perceiving the other devices and
the \emph{communication} ($\chi$) component is responsible for sending the data to the alert system.
%
The latter represents the alert system and consists of the following pulverized components:
$\beta$, $\kappa$, $\chi$, and $\alpha$.
%
The \emph{behaviour} ($\beta$) component is responsible for evaluating the meand distance between the devices,
the \emph{actuators} ($\alpha$) is responsible for triggering the alarm showing a color in the screen,
and the \emph{communication} ($\chi$) component is responsible for receiving the data from the wearable devices.

@@

\subsection{Large scale: smart city application}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{acronym}
\usepackage{listing-style}
\usepackage[hidelinks]{hyperref}

@@

\begin{abstract}
In recent years, we witnessed a fast-paced evolution of the infrastructure hosting distributed computations.
%
Modern applications are designed to be executed on very diverse devices
and to be deployed on infrastructures composed of devices ranging from cloud servers to mobile and IoT devices,
constituting together a cloud-edge continuum.
%
The availability of such an infrastructure opens to better resource utilisation and performance,
but, contextually, introduces new challenges to software designers,
as applications must be conceived to be able to adapt their deployment to changing conditions.
%
In this paper,
we introduce a framework for the development of distributed systems
based on the concept of \emph{pulverisation},
meant to neatly separate business logic and deployment concerns,
allowing applications to be defined independent of the infrastructure they will execute upon.
%
The framework is based on a domain-specific language capturing,
in a declarative fashion,
pulverised application components, device capabilities, resource allocation, and (runtime re-) configuration policies.
%
The framework, implemented in Kotlin multiplatform and available as open source,
is then evaluated in a small-scale real-world demo and in a city-scale simulated scenario.
\end{abstract}

@@

In this section we present a simple scenario where the pulverization framework is used to implement a crowd alert system:
we simulate a laboratory where a safety system warns people when they are too close to each other.
%
Each person is equipped with a wearable device that is able to detect the distance from other devices and send the distances data to the
alert system.
%
The people in the laboratory must observe a safety distance, and the system warns them when the distance is not respected by showing a red light
when they are too close to each other, and a green color when the distance is respected (see~\Cref{fig:crowd-alert}).
%
\begin{figure*}[ht]
    \centering
    \includegraphics[width=.8\textwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in the~\Cref{sec:small-scale-crowd-alert}
        where more the people are far from each other, more the color of the screen is green.
        More the people are close to each other, more the color of the screen is red.
        The blue dot represents the wearable device and the link between the devices represents the distance between them.
        The rectangle represents the monitor in the laboratory which shows the congestion level of the laboratory (via the color described above).
    }
    \label{fig:crowd-alert}
\end{figure*}
%
The system is composed of two kind of devices: \emph{wearable} and \emph{laboratory}.
%
The former represents the wearable devices that is worn by the people, and consists of the following pulverized components:
$\beta$, $\chi$, and $\sigma$.
%
The \emph{behaviour} ($\beta$) component is responsible for converting the raw data from the sensor into the distance
between the device and the others; the \emph{sensors} ($\sigma$) component is responsible for perceiving the other devices and
the \emph{communication} ($\chi$) component is responsible for sending the data to the alert system.
%
The latter represents the alert system and consists of the following pulverized components:
$\beta$, $\kappa$, $\chi$, and $\alpha$.
%
The \emph{behaviour} ($\beta$) component is responsible for evaluating the meand distance between the devices,
the \emph{actuators} ($\alpha$) is responsible for triggering the alarm showing a color in the screen,
and the \emph{communication} ($\chi$) component is responsible for receiving the data from the wearable devices.

@@

\subsection{Large scale: urban event}
